%-------------------------
% Resume in Latex
% Author : Amlaan Bhoi
% Adapted from: Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=blue,  %choose some color if you want links to stand out
    urlcolor=blue
}

\usepackage[charter]{mathdesign} % Bitstream Charter
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[
top    = 2.75cm,
bottom = 2.75cm,
left   = 1.20cm,
right  = 1.20cm]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \small \textbf{{\LARGE Mengyao Huang}} \\    
  1929 Plymouth Road APT 4027, Ann Arbor, MI 48105 \\
  (+1) (734) 263-3205 $\vert$ huangmy@umich.edu $\vert$ Github: \href{https://github.com/MengyaoHuang}{https://github.com/MengyaoHuang}
\end{center}

% $\vert$ Github: \href{https://github.com/MengyaoHuang}

%-----------EDUCATION-----------------
\shorterSection{Education}
   \resumeSubHeadingListStart
    \resumeSubheading{University of Michigan}{Ann Arbor, MI}{Department of Mathematics}\hfill
    \vspace{-18pt}
    \resumeSubheading{}{}{Master of Science in Quantitative Finance and Risk Management \&
      Data Science Certificate Program;  GPA: 3.6/4}{Sept. 2017 - May. 2019}{        
      \resumeItemNoBullet{Relevant Courses}{Stochastic Analysis, Statistical Learning, Data Mining, Machine Learning, AI Foundations, Data  Manipulation and Analysis, Financial Mathematics, Computational Finance, Special Topics in Marketing(Doctoral), Quantitative Research in Marketing(Doctoral)}
    }
    \vspace{6pt}
    
    \resumeSubheading{Dalian University of Technology}{Dalian, China}{School of Mathematical Sciences}\hfill
    \vspace{-18pt}
    \resumeSubheading{}{}{Bachelor of Science in Mathematics and Applied Mathematics \& 
      	Bachelor of Science in Finance;  GPA: 3.6/4}{Sept. 2013 - Jun. 2017}
	 \resumeItemNoBullet{Relevant Courses}{Calculus, Advanced Algebra, Ordinary Differential Equations, Optimization Methods, Complex Analysis, Real Analysis, Functional Analysis, Multivariate Statistical Analysis, Time Series Analysis, Game Theory, Econometrics}
   \resumeSubHeadingListEnd
\vspace{8pt}


%-----------RESEARCH INTERESTS---------
\shorterSection{Research Interests}
    \resumeSubHeadingListStart
   % \resumeItemNoBullet{}
   \hspace{-12pt}
   {\small \sl Machine Learning and Statistical Learning in Marketing Research, Recommendation System}
     \resumeSubHeadingListEnd
\vspace{0pt}

%-----------Research Experience-----------------
\shorterSection{Research and Working Projects}
  \resumeSubHeadingListStart
%%%% Research Experience 1 %%%%
      \resumeSubItem{Marketing Research}{Advisor: Fred M.Feinberg
		   \hspace{270pt}
	 {\textit{May. 2018 - present} \par}
	 % Add a summary for research tools here
	 {\sl \textbf{Topics}: Data Preprocessing, Machine Learning Algorithms, Bayesian Inference, Matrix Factorization, Choice Model}
      \begin{itemize}
      % Models: clustering/classification
      % Research tools: Python Pandas; Python ggplot and matplotlib
      % working project:
      \item Integrated databases and performed data cleaning with Python Pandas including outliers filtering, missing data imputation, categories reduction, dummy variables creation and data normalization
      \item Operated data visualization for CRM database with Python ggplot and matplotlib; calculated statistical metrics for further inference
      \item Implemented customer clustering/classification algorithm for CRM database with K-means, K-modes (GOWER distance based), Random Forest and Naive Bayes in Python and package "MatchIt" in R
      \vspace{8pt}
      \item Learned \textbf{Bayesian Mixture Model}, \textbf{EM Algorithm}, \textbf{Gibbs Sampling} and \textbf{Multinomial Logit Model} with mixed effect
      \item Implemented Multinomial Logit Model, \textbf{Nested Logit Model} (with/without cross validation), \textbf{Linear Mixed Effects Model} and \textbf{PCA} analysis with R and Python scikit-learn \& mnlogit
      \vspace{8pt}
	  \item Implemented \textbf{Variational Inference} with Normalizing Flows algorithm (Rezende \& Mohamed, 2016) in Python with MNIST dataset
	  \item Wrote literature review abstract related to Low-rank \textbf{Matrix Approximation}, \textbf{Latent Factors Interpretation} and \textbf{Recommendation System}; implemented \textbf{Bayesian Matrix Factorization} (with/without side information) in Python with MovieLens dataset
	  \item Implemented \textbf{Variational Autoencoder} and \textbf{Gaussian Mixture Model} in Pyro (with/without Poutine library)
	  \vspace{8pt}
	  \item Performed \textbf{Discrete Choice Model} analysis in the context of Choice Set Formation (Salisbury \& Feinberg, 2012; Bruth et al., 2016); helped with R package \textbf{DCmods} modification, output aggregation and visualization
      \end{itemize}
      
    {\sl \textbf{Working Projects}:}
    \begin{itemize}
        \item  Construction and interpretation of DCmods vignettes
        \item  Variational Autoencoder application in data fusion and Unbiased Implicit VI implementation
        \item  Matrix Factorization application in marketing data imputation
    \end{itemize}
  }


%%%% Research Experience 2 %%%%
      \resumeSubItem{Social Structure research in Strategy}{Advisor: Michael Jensen
                   \hspace{210pt}
	  {\textit{Mar. 2019 - present} \par}
      {\sl \textbf{Topics}: Web Scraping and Data Integration, Selenium Automation Testing, Natural Language Processing}
        \begin{itemize}
            \item Performed web scraping (IMDb, Wikipedia, BookMyShow, Box Office Mojo and etc) to collect seasonality info and film directors' demographic info, trivia \& images with Python Pandas \& Beautiful Soup and VBA in Excel
            \item Collected user/critic ratings and comments for films; implemented transparent text analysis with Linguistic Inquiry and Word Count (LIWC) and Topic Modeling with Python scikit-learn (Latent Dirichlet Allocation)
            \item Set up scraping program through Selenium driver to automate login \& searching process; collected rankings of casts and directors by DOM and HTML parsing and Text pattern matching
        \end{itemize}
     }

%%%% Research Experience 3 %%%%
    \resumeSubItem{Optimization in Principal-Agent Problem}{Advisor: Nicolas Hernandez
                    \hspace{169pt}
	  {\textit{Nov. 2017 - Oct. 2018}}
	  \vspace{-5pt}
        \begin{itemize}
      \item Implemented nonpolynomial approach of actions related agent's utility maximization problem (Renner \& Schmedders, 2015)
	\item Tested algorithm efficiency and global optimality with both MATLAB GloptiPoly and modified fmincon method
	\end{itemize}
	}
	
%%%% Research Experience 4 %%%%
\resumeSubItem{Optimization in Asset Liability Management}{Advisor: Guotai Chi
                    \hspace{185pt}
	  {\textit{Nov. 2015 - Jun. 2017}}
	  \vspace{-5pt}
        \begin{itemize}
      \item Implemented optimization algorithm of worst-case Conditional Value-at-Risk(WCVaR) under mixture distribution and kernel density estimation (Zhu \& Fukushima, 2009) with MATLAB
	\item Modified robust portfolio optimization by introducing credit rating transition matrix
	\end{itemize}
	}

%%%% Research Experience 5 %%%%
\resumeSubItem{Complex Ecosystem Evolution Model}{Advisor: Qiuhui Pan
                    \hspace{210pt}
	  {\textit{Mar. 2015 - May. 2016}}
	  \vspace{-5pt}
        \begin{itemize}
      \item Introduced external factors like water distribution to complex ecosystem; adopted Partial Differential Equations to measure energy flow and implemented dynamic Monte Carlo (DMC) simulation with MATLAB
	\end{itemize}
	}
  \resumeSubHeadingListEnd
\vspace{8pt}

%-----------EXPERIENCE-----------------
\shorterSection{Professional Experience}
  \resumeSubHeadingListStart
   %%%%% Experience 1 %%%%%
      \resumeSubheading
    {Washtenaw Community College} {Ann Arbor, MI}
    {Research Analyst in Institutional Research and Analytics Dept}{Aug. 2019 - present}
\resumeItemNoBullet{Mentor}{Mourad Roger}
    \begin{itemize}
        \item Updated databases \& annual reports using Microsoft Access and Power BI
  	    \item Conducted \textbf{Excess Credits Research} in community college system by examining credits distributions in the context of particular degree programs (Zeidenberg, 2012); further improved accuracy by considering transferred credits and candidates with more degrees
  \end{itemize}

 %%%%% Experience 2 %%%%%
    	\resumeSubheading
      {BOHAI Securities Co., Ltd}{Tianjin, China}
      {Researcher in Quantitative Trading Division}{Jul. 2016 - Aug. 2016}
        \begin{itemize}
          \item Improved stock price cycles estimation by implementing weighted Fourier Transform algorithm; strengthened the performance of quantitative timing model by adopting year-on-year series and adjusting tuning parameters including length of subsequences
      \end{itemize}
      
 %%%%% Experience 3 %%%%%
      	\resumeSubheading
      {AXA Group, Hong Kong Branch}{Hong Kong, China}
      {Assistant Analyst in Market Research Department}{Jan. 2016 - Feb. 2016}
        \begin{itemize}
          \item Developed trading strategies based on Fundamental Analysis and indicators including MACD, KDJ, SAR and price-volume relationship
        	\item 
          {Analyzed financial time series in EViews; applied multivariate linear regression model and GARCH model to predict Hang Seng Index
          }
      \end{itemize}
  \resumeSubHeadingListEnd
\vspace{8pt}

%--------Other Activities-----------
\shorterSection{Honors and Activities}
\resumeSubHeadingListStart
    \vspace{-8pt}
    \resumeSubheading
    {}{}{Third prize in National Mathematical Modeling Contest}{Nov. 2015}
    \vspace{-15pt}
    \resumeSubheading
    {}{}{First prize in Mathematical Contest in Modeling in Northeastern China (Top 5\%)}{May. 2015}
    \vspace{-15pt}
    \resumeSubheading
    {}{}{DUT Technological Innovation Award (Top 5 out of 180)}{Oct. 2014}
    \vspace{-10pt}
    
    \resumeSubheading
    {}{}{President of DUT Mathematical Modeling Association}{Sept. 2015 - Sept. 2016}
    \vspace{-15pt}
    \resumeSubheading
    {}{}{(DUT Outstanding Student Association Award)}{May. 2016}
    \vspace{-15pt}
    \resumeSubheading
    {}{}{Certificate of DUT Innovation Practice Training 3-year Program (Mathematical Modeling track)}{Jul. 2016}
    \vspace{-15pt}
    \resumeSubheading
    {}{}{Certificate of Qualification in AXA SL financial Group of ZhuoHao Business School}{Feb. 2016}

\resumeSubHeadingListEnd
\vspace{8pt}

%-----------Personal-----------------
\shorterSection{Personal}
  \resumeSubHeadingListStart
  \small
    \item
     \textbf{Languages}{: Mandarin Chinese (native), English (TOEFL iBT: 105, GRE: 325+4.5)}
     \vspace{-5pt}
    \item
     \textbf{Skills}{: Fluent in Python, Pytorch-Pyro, R, MATLAB and C++/C;  intermediate in SQL, Stan, Microsoft Access, and EViews}
     \vspace{-5pt}
    \item
     \textbf{Interests}{: Sketch, Play squash, Social psychology(recent)}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}